Fluent statistical computing interfaces for biological data analysis

### 2020-07-19 Rmd/05-embeddings.Rmd
update pdf

disply_vid_latex <- function(key, lookup) {
    video <- lookup[lookup$key == key, ]
    glue::glue(
    "\\begin{{center}}
   \\includemedia[
    activate=pageopen,
    width=640pt,
    height=400pt,
    keepaspectratio=true,
    addresource={video},
    flashvars={{%
      src={video}
      &scaleMode=stretch}
  ]{{}}{{StrobeMediaPlayback.swf}}
  \\end{{center}}",
  video = video[["path"]]
  )
}

>>>>

display_vid_latex <- function(key, lookup) {
    video <- lookup[lookup$key == key, ]
    glue::glue(
    "\\begin{{center}}
   \\includemedia[
    width=0.6\\linewidth,
    height=0.4\\linewidth,
    keepaspectratio=true,
    addresource={video},
    flashvars={{%
      source={video}
      &autohide=1
      &autoPlay=true
      &loop=true}
  ]{{}}{{VPlayer.swf}}
  \\end{{center}}",
  video = video[["path"]]
  )
}
